xwMOOC 딥러닝

### 2018-05-09 ms-azure-computer-vision.Rmd
compile...

# 1. 데이터 받아오기 -----
api_key <- "5463d62395e84bd1a9e6cb3e379ce692"
api_endpoint_url = "https://eastasia.api.cognitive.microsoft.com/vision/v1.0/analyze"

@@

api_key <- "5463d62395e84bd1a9e6cb3e379ce692"
api_endpoint_url <- "https://eastasia.api.cognitive.microsoft.com/vision/v1.0/analyze"
visual_features <- "Description,Adult"

>>>>

# 1. 데이터 받아오기 -----
api_key <- "7bbbe18842a14a1cb6da67a23095c2fc"
api_endpoint_url = "https://eastasia.api.cognitive.microsoft.com/vision/v1.0/analyze"

@@

api_key <- "7bbbe18842a14a1cb6da67a23095c2fc"
api_endpoint_url <- "https://eastasia.api.cognitive.microsoft.com/vision/v1.0/analyze"
visual_features <- "Description,Adult"
